Estimating duration in the presence of misclassification

### 2024-02-26 introduction.tex
first attempt in outlining intro

@@

No single quantity summarises the full state of an epidemic, and no single data source fully informs all quantities of interest.
Therefore, a range of metrics and surveillance systems are required to understand the state of an epidemic and the danger of a pathogen (a pathogen is any biological agent that can cause disease).

@@

Growth rates and reproduction numbers only provide information on how an epidemic is changing.
\emph{Incidence} is the primary quantity of interest for the current (or historical) magnitude of a pandemic.

@@

To translate any of these quantities into the burden of the disease, a measure of severity is required.
For example, the IFR (infection fatality rate), the proportion of infected individuals who die.
Severity does not feature in this thesis, but it is important to note that it is a key component of understanding the burden of a pandemic.\todo{maybe reword sentence}

>>>>

\todo[inline]{Maybe talk about pandemic v epidemic v outbreak terminology?}

@@

No single metric summarises the full state of an epidemic, and no single data source fully informs all metrics of interest.
Therefore, a range of metrics and surveillance systems are required to understand the state of an epidemic and the danger of a pathogen (a pathogen is any biological agent that can cause disease).

@@

Growth rates and reproduction numbers only provide information on how an epidemic is changing.
\emph{Incidence} is the primary metric for the magnitude of a pandemic.
See \cref{E-inc-prev:sec:definitions} for a formal definition of incidence and prevalence.

@@

To translate incidence into the burden of the disease, a measure of severity is required.
For example, the IFR (infection fatality rate), the proportion of infected individuals who die.
% Severity does not feature in this thesis, but it is important to note that it is a key component of understanding the burden of a pandemic.\todo{maybe reword sentence}
